---
title: "Performance Evaluation All at Once"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## You are welcome to use my new package perflite

It is a one step, easy to use package to evaluate any performances of machine learning algorithm.

Notice that the first version of this package is develped using **6 hours of one day**.
And it could already realize the one step automatic performance evaluation on multiple datasets and multiple machine learning methods (with cross validation + parallel computation).

## Install this package on your PC or server

You can download this package right now from github:

```{r , eval=FALSE}
devtools::install_github("ZhenWei10/perflite")
```

## Run a performance evaluation with the example files in package

```{r,cache=TRUE,warning=FALSE}
library(perflite)
perf_results <- performance_cv(example_y,example_X)
```

##Check the performance tables.
```{r,warning=FALSE}
library(knitr)
kable(perf_results[[1]],
       format = "html", 
       caption = names(perf_results)[1]) 
```

```{r}
kable(perf_results[[2]],
       format = "html", 
       caption = names(perf_results)[2]) 
```

##A plot of ROC curve is automatically saved under the current directory.

```{r pressure, echo=FALSE, fig.cap="The whole analysis requires only one function.", out.width = '100%'}
knitr::include_graphics("/Users/zhenwei/Documents/GitHub/perflite/ROC_cv.pdf")
```

```{r}
sessionInfo()
```


